What entries are in which files?

### 2017-02-20 verification/all-pde-days/all-pde-days.Rmd
verification

There is a clear pattern by day:
```{r plot_days}
d11 %>%
  ggplot(aes(x=date, y=count)) +
  geom_line() + geom_point() +
  xlab('day of the year 2011') + ylab('PDEs on that day') +
  theme_minimal()
```

@@

Which days are the ones that have large z-scores?
```{r outliers}
d11 %>%
  select(day_of_week, date, day_of_week_z_score) %>%
  filter(abs(day_of_week_z_score) >= 2) %>%
  arrange(day_of_week) %>%
  kable
```

@@

>>>>

There is a clear pattern by day:
```{r plot_days, echo=FALSE}
d11 %>%
  ggplot(aes(x=date, y=count)) +
  geom_line() + geom_point() +
  xlab('day of the year 2011') + ylab('PDEs on that day') +
  theme_minimal()
```

@@

Which days are the ones that have large z-scores?
```{r outliers, echo=FALSE}
d11 %>%
  select(day_of_week, date, day_of_week_z_score) %>%
  filter(abs(day_of_week_z_score) >= 2) %>%
  arrange(day_of_week) %>%
  kable
```

@@

# 2012

Was there something weird happening in 2012?

```{r load_2012}
d12 = read_tsv('pde_date_counts_2012.tsv') %>%
  mutate(date=dmy(date)) %>%
  mutate(week_n=week(date)) %>%
  mutate(day_of_week=date %>% weekdays %>% factor(levels=dow_levels, ordered=TRUE)) %>%
  group_by(day_of_week) %>%
  mutate(day_of_week_z_score=as.vector(scale(count))) %>%
  ungroup()
```

```{r plot_2012_days}
d12 %>%
  ggplot(aes(x=date, y=count)) +
  geom_point() + geom_line() +
  theme_minimal()
```

```{r}

bind_rows(d11 %>% mutate(data_year=2011),
          d12 %>% mutate(data_year=2012)) %>%
  mutate(data_year=factor(data_year)) %>%
  ggplot(aes(x=date, y=count, color=data_year, group=data_year)) +
  geom_point() + geom_line()
```

### 2017-02-20 verification/pde-years/pde-years.Rmd
verification

---
title: "Differences in Medicare years"
author: "Scott Olesen"
date: "2/13/2017"
output:
  pdf_document:
    fig_caption: yes
---

@@

There is a clear trend in the Medicare Part D data: more claims are reported in 2012 compared with 2011, 2013, and 2014.

>>>>

---
title: "What entries are in which files?"
author: "Scott Olesen"
output: html_document
---

@@

The 2012 PDE data seems to be exceptional. Why is this the case?
